---
title: "Scatter and 3D plots with Plotly pacakge"
author: "Aijun Zhang"
date: "2023-05-29"
output: html_document
---

## Introduction
Create a web page presentation using R Markdown that features a plot created with Plotly. 
Using the **"mtcars"** dataset. The data was extracted from the 1974 Motor Trend US magazine, and comprises fuel consumption and 10 aspects of automobile design and performance for 32 automobiles (1973–74 models).

## Plotly plot

### Load library and dataset
```{r library, message=F}
library(plotly)
```

### Load the dataset and preprocess
```{r data and preprocess}
df <- mtcars
df <- within(df, {
  vs <- factor(vs, labels = c("V", "S"))
  am <- factor(am, labels = c("automatic", "manual"))
  cyl  <- ordered(cyl)
  gear <- ordered(gear)
  carb <- ordered(carb)
})
```

### Plot the interactive plot with plotly
it shows the relation between miles/gallon(mpg), 1/4 mile tiem(qsec) between different transmission auto and manual(am) which in the category of carburetor numbers(carb).
```{r scatter, , warning=F}
fig <- df %>%
  plot_ly(
    x = ~qsec,
    y = ~mpg,
    size = ~hp,
    color = ~am,
    colors = c("red","black"),
    frame = ~carb,
    text = ~mpg,
    hoverinfo = "text",
    type = 'scatter',
    mode = 'markers'
  )
fig <- fig %>% layout(
  xaxis = list(
    type = "log"
  )
)

fig
```

### 3D plot with plotly
```{r 3d}
fig1 <- plot_ly(df, x = ~mpg, y = ~hp, z = ~wt, type = 'scatter3d', mode = 'lines+markers',
              line = list(width = 10, color = ~gear, reverscale = FALSE))

fig1
```


Plotly’s R graphing library makes interactive, publication-quality graphs. It can be used to make a variety of graphics includeing: line plots, scatter plots, area charts, bar charts, error bars, box plots, histograms, heatmaps, subplots, multiple-axes, and 3D (WebGL based) charts.


-End-
